---
title: "Visualize 'supreme' objects"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Visualize 'supreme' objects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(supreme)
library(magrittr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

This vignette is about styling graphs created from supreme objects.

```{r}
paths <- example_app_path()
s <- supreme(src_file(paths))
s
```

Create entity-relationship diagram:
```{r}
graph(s)
```

Style graph:

```{r, eval=FALSE}
# graph(s, style = list(name = "server", fill = "#ff0", linetype = "dashed"))
```

Example: Style modules whose name ending with 'slider':

```{r}
#s_df <- as.data.frame(s) # turn supreme object to data.frame
#graph(s, style = list(name = grep("^slider", s_df$name), fill = "#ff0"))
```

A good use of changing styles could be for focusing on particular modules.
An example tries to make parent and child of a module explicit:
```{r}
# arrange parent & child
```

You can have a custom options for the graph:
```{r}
# graph(s, options = list(
#   direction = "right", 
#   fontSize = 10, 
#   title = "Model customer plot")
# )
```

You can also use `%>%` pipes from the
[magrittr](https://cran.r-project.org/package=magrittr) package:

```{r}
supreme(src_file(paths)) %>%
  graph()
```

